My title

### 2024-10-24 paper/paper.qmd
Update typos.

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Xuanle Zhou
  - Yongqi Liu
  - Yuxuan Wei
thanks: "Code and data are available at: [https://github.com/wyx827/2024USpresidentialelection.git]."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

#install.packages("tidymodels")

library(tidyverse)
library(ggplot2)
library(rstanarm)
library(knitr)

@@

### end date

@@

# Interpretation of Coefficients:

- Intercept (\beta_0): This is the predicted Trump polling percentage when all predictors (numeric grade, sample size, state, transparency score, and end date) are at their baseline or zero value.
- Numeric Grade (\beta_1): This coefficient measures how much Trump’s polling percentage changes as the pollster’s numeric grade increases. A positive and significant coefficient would indicate that higher-rated pollsters report better polling numbers for Trump, while a negative coefficient would suggest the opposite.
- Sample Size (\beta_2): This measures the impact of the number of respondents on Trump’s polling percentage. A positive coefficient would indicate that larger sample sizes are associated with higher polling percentages for Trump.
- State (\beta_3): The coefficients for the state variable represent differences in Trump’s polling percentage in each state compared to the reference state (baseline category). For example, if the coefficient for Florida is negative, it means Trump polls lower in Florida compared to the reference state.
- Transparency Score (\beta_4): This coefficient shows how much Trump’s polling percentage is affected by the transparency of the poll. A positive coefficient would indicate that polls with higher transparency tend to report higher polling percentages for Trump, whereas a negative coefficient would imply the opposite.
- End Date (\beta_5): The end date is a time-related variable, capturing trends over time. A positive and significant coefficient would suggest that Trump’s polling percentage has increased as the election date approaches, while a negative coefficient would suggest a decrease in his polling numbers over time.

@@

The posterior distributions of the parameters allow us to quantify the uncertainty around each effect:\

* The coefficient for end_date informs us about how Trump’s polling percentages have evolved over time. A positive coefficient would suggest an upward trend, while a negative coefficient would indicate a decline.\
* The coefficient for numeric_grade captures the impact of pollster quality on the polling percentage. High-quality pollsters may produce different estimates compared to lower-quality ones.\
* The state-level effects account for regional differences in Trump’s support. Some states may show significantly higher or lower levels of support, even after adjusting for the time of the poll and pollster quality.

# Model Evalutation
- R-squared
@tbl-summary shows the summary table for the model. And then evaluate it on the test set. It appears as though the model is having difficulty identifying Trump supporters.
```{r}
#| echno: False
#| label: tbl-summary
#| tbl-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

library(knitr)
regression_model<-readRDS(here::here("models/regression_model.rds"))
summary<-summary(regression_model)
# Extract the coefficients (which can be formatted as a table)
coefficients_table <- summary$coefficients

# Display the coefficients table using kable
kable(coefficients_table, digits = 3, caption = "Regression Model Coefficients")
```

# Diagnostic plots for the model
```{r}
#| echno: false
#| label: fig-diagnosis-1
#| tbl-cap: Linear Regression Assumptions hold.
#| echo: false
#| warning: false
#| message: false

par(mfrow = c(2, 2))  
plot(regression_model)
```

```{r}
#| echno: false
#| label: fig-diagnosis-2
#| tbl-cap: Linear Regression Assumptions hold.
#| echo: false
#| warning: false
#| message: false

#library(car)
#vif(regression_model)
```

### Model justification

@@

```{r tbl-prediction, echo=FALSE, warning=FALSE, message=FALSE}
#| echno: false
#| label: tbl-prediction
#| tbl-cap: Prediction for Trump
#| echo: false
#| warning: false
#| message: false

@@

# Create the table using kable
kable(state_predictions[, c("state", "predicted_percent_trump", "electoral_votes", "winner")], 
      col.names = c("State", "Trump Predicted %", "Electoral Votes", "Winner"), 
      digits = 2, 
      caption = "Prediction for Trump by State")

@@

## Predicted Electoral Outcomes by State
The following map (@fig-statemap) shows the predicted winner for each state in the 2024 U.S. Presidential Election, based on the regression model's predicted vote percentages for Trump and Harris.
```{r tbl-prediction, echo=FALSE, warning=FALSE, message=FALSE}
#| echno: false
#| label: fig-statemap
#| tbl-cap: Predicted Winner of 2024 US Presidential Election by State
#| echo: false
#| warning: false
#| message: false
#| 
# Load necessary libraries
library(usmap)

@@

## Weaknesses of What Was Done
While the model offers a useful prediction, it has limitations. It relies heavily on past voting data, which may not fully capture future changes in voter behavior or external factors that could affect the election. The model also simplifies the election by focusing on state-level percentages, without accounting for variables such as turnout, third-party candidates, or unexpected political shifts. Additionally, the assumption that past voting patterns will continue might not be accurate in a rapidly changing political landscape.

@@

## Weaknesses and next steps
The logistic regression model is limited by the lack of interaction terms between states, which may obscure regional trends or external factors that influence neighboring states. Additionally, the model assumes that polling data accurately reflects voter intentions, but biases or missing data in key regions could affect the predictions.

@@

# Additional data details

@@

## Posterior predictive check

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

@@

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2
library(caret)
library(rstanarm)
library(ggplot2)
library(dplyr)
# Split the data into training (70%) and test (30%) sets
set.seed(853)  # For reproducibility

@@

# Acknowledgements
@citeR

>>>>

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Xuanle Zhou
  - Yongqi Liu
  - Yuxuan Wei
thanks: "Code and data are available at: https://github.com/wyx827/2024USpresidentialelection.git."
date: today
date-format: long
toc: true
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

#install.packages("tidymodels")
#install.packages("usmap")
library(tidyverse)
library(ggplot2)
library(rstanarm)
library(knitr)
library(usmap)

@@

### End Date

@@

## Interpretation of Coefficients

- Intercept ($\beta_0$): This is the predicted Trump polling percentage when all predictors (numeric grade, sample size, state, transparency score, and end date) are at their baseline or zero value.
- Numeric Grade ($\beta_1$): This coefficient measures how much Trump’s polling percentage changes as the pollster’s numeric grade increases. A positive and significant coefficient would indicate that higher-rated pollsters report better polling numbers for Trump, while a negative coefficient would suggest the opposite.
- Sample Size ($\beta_2$): This measures the impact of the number of respondents on Trump’s polling percentage. A positive coefficient would indicate that larger sample sizes are associated with higher polling percentages for Trump.
- State ($\beta_3$): The coefficients for the state variable represent differences in Trump’s polling percentage in each state compared to the reference state (baseline category). For example, if the coefficient for Florida is negative, it means Trump polls lower in Florida compared to the reference state.
- Transparency Score ($\beta_4$): This coefficient shows how much Trump’s polling percentage is affected by the transparency of the poll. A positive coefficient would indicate that polls with higher transparency tend to report higher polling percentages for Trump, whereas a negative coefficient would imply the opposite.
- End Date ($\beta_5$): The end date is a time-related variable, capturing trends over time. A positive and significant coefficient would suggest that Trump’s polling percentage has increased as the election date approaches, while a negative coefficient would suggest a decrease in his polling numbers over time.

@@

The posterior distributions of the parameters allow us to quantify the uncertainty around each effect:\
* The coefficient for end_date informs us about how Trump’s polling percentages have evolved over time. A positive coefficient would suggest an upward trend, while a negative coefficient would indicate a decline.\
* The coefficient for numeric_grade captures the impact of pollster quality on the polling percentage. High-quality pollsters may produce different estimates compared to lower-quality ones.\
* The state-level effects account for regional differences in Trump’s support. Some states may show significantly higher or lower levels of support, even after adjusting for the time of the poll and pollster quality.

## Model Justification
@tbl-summary shows the summary table for the model. And then evaluate it on the test set. It appears as though the model is having difficulty identifying Trump supporters.
```{r}
#| echno: False
#| label: tbl-summary
#| tbl-cap: Regression Model Estimate Summary
#| echo: false
#| warning: false
#| message: false

regression_model<-readRDS(here::here("models/regression_model.rds"))
summary<-summary(regression_model)

# Extract the coefficients to form a table
coefficients_table <- summary$coefficients

# Display the first 10 rows of the coefficients table using kable, formatted to 4 decimal places
kable(head(coefficients_table, 10), digits = 4)
```

### VIF Evaluation
@tbl-vif displays that

```{r}
#| echno: false
#| label: tbl-vif
#| tbl-cap: VIF shows a reasonable output.
#| echo: false
#| warning: false
#| message: false

library(car)
kable(vif(regression_model))
```

@@

```{r tbl-prediction}
#| echno: false
#| label: tbl-prediction
#| tbl-cap: Prediction for Trump and Harris by Electoral College
#| echo: false
#| warning: false
#| message: false

@@

# Create the table using kable
kable(state_predictions[, c("state", "predicted_percent_trump", "electoral_votes", "winner")], 
      col.names = c("State", "Trump Predicted %", "Electoral Votes", "Winner"), 
      digits = 2)

@@

## Predicted Electoral Outcomes by State
The following map (@fig-statemap) shows the predicted winner for each state in the 2024 U.S. Presidential Election, based on the regression model's predicted vote percentages for Trump and Harris.

```{r tbl-prediction}
#| echno: false
#| label: fig-statemap
#| tbl-cap: Predicted Winner of 2024 US Presidential Election by State
#| echo: false
#| warning: false
#| message: false

@@

@@

## Weaknesses and Next Steps
While the model offers a useful prediction, it has limitations. It relies heavily on past voting data, which may not fully capture future changes in voter behavior or external factors that could affect the election. The model also simplifies the election by focusing on state-level percentages, without accounting for variables such as turnout, third-party candidates, or unexpected political shifts. Additionally, the assumption that past voting patterns will continue might not be accurate in a rapidly changing political landscape. The logistic regression model is limited by the lack of interaction terms between states, which may obscure regional trends or external factors that influence neighboring states. Additionally, the model assumes that polling data accurately reflects voter intentions, but biases or missing data in key regions could affect the predictions.

@@

@@

```{r}
#| echno: false
#| label: fig-diagnosis-1
#| tbl-cap: Linear Regression Assumptions hold
#| echo: false
#| warning: false
#| message: false

par(mfrow = c(2, 2))  
plot(regression_model)

@@

## Multicolinearity Check

@@

# Acknowledgements
@citeR
Thanks to Open AI and ChatGPT 4.0 is used to write the analysis of the paper.
